---
title: "BCF for Saga/Match Treatment Heterogeneity"
author: ""
#date: "May 29, 2020"
output: pdf_document
fontsize: 9pt
geometry: margin=0.75in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F, message = F)


use_clusters = F
no_dupes = T

library(kableExtra)
library(ggplot2)
library(knitr)
library(dplyr)
library(grf)

as_factor <- forcats::as_factor

Sys.setenv(
  PATH = paste(
    "/export/opt/texlive/2018/bin/x86_64-linux",
    Sys.getenv("PATH"),
    sep = ":"
  )
)




all_bart_models <- readRDS('combined_bart_splitsample_models.Rds')

```

This document presents the current `BART` (Bayesian Additive Regression Trees) analysis of treatment heterogeneity. We present results for the following outcomes:

* Math Test Scores
* Math Class Failures
* Math GPA
* Reading Test Scores
* Non-math GPA
* Graduated on-time
* Ever graduated
* 11th Grade Math GPA



We use all covariates from our main analyses (except for randomization block). These include gender, age, learning disability, free lunch recipient, race, baseline grade level, GPA, baseline test performance (and within-baseline-school math test decile), days absent from school, disciplinary incidents, including suspensions, and arrests.

\newpage

<!-- ## Section 1: with imputing block means for missing covariates -->
<!-- ```{r, results='asis', include=T, echo=F, fig.height=2} -->
<!-- final_forests_imputed %>% print_forests() -->

<!-- ``` -->

<!-- \newpage -->



<!-- # Decile Heatmaps -->

```{r, results='asis', include=T, echo=F, fig.height=3.5, fig.width=7,  warning=F}
# for (comparison in all_pte_quantile_plots){
#   
#   for (plot in comparison){
#     cat('\n')
#     print(plot)
#     cat('\n')
#   }
#       
#  
#     cat('\\newpage')
# }


for (outcome in names(all_bart_models)){
  cat('\n ')
  cat('# Outcome: ', outcome, " \n")
  
  current_model <- all_bart_models[[outcome]]
  model_item_names <- names(current_model)
  i = 0
  for (item in current_model){
    i = i+1
    # if there's a splitsample pvalue, add adjusted pvalue column
    current_name <- model_item_names[i] %>% stringr::str_replace_all("_", " ")
    if (names(item) %>%  stringr::str_detect('p.value_') %>% max == 1){
      item <- item %>% mutate(adj.pval = 2*p.value_median)
    }
    
    
      item %>%
      kable(booktabs=T, digits=3, escape=T, linesep="",
            caption = paste0(current_name, " - ", outcome)) %>%
      kable_styling(latex_options = c(#'striped',
      'HOLD_position')) %>% print()
  
  }
 
  
   cat('\n')
   cat('\\newpage')
}

```