---
title: "Causal Forests for Saga/Match Treatment Heterogeneity"
author: ""
#date: "May 29, 2020"
output: pdf_document
fontsize: 9pt
geometry: margin=0.75in
header-includes:
  - \usepackage{xcolor}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F, message = F)

set.seed(20201117)

use_clusters = F
no_dupes = T

library(kableExtra)
library(ggplot2)
library(knitr)
library(dplyr)
library(grf)

as_factor <- forcats::as_factor

Sys.setenv(
  PATH = paste(
    "/export/opt/texlive/2018/bin/x86_64-linux",
    Sys.getenv("PATH"),
    sep = ":"
  )
)

source('mltx_globals.R')
source('isr_outcomes_and_labels_list.R')

fullsample_models <- readRDS('all_fullsample_cf_models.Rds')
splitsample_models <- readRDS('combined_final_grf_splitsample_models.Rds')

```

This document presents the current `GRF` (Generalized Random Forests) Causal Forest analysis of treatment heterogeneity. We present results for the following outcomes:

* Math Test Scores
* Math Class Failures
* Math GPA
* Non-math GPA (calculated various ways)


We use all covariates from our main analyses (except for randomization block, which enters into this analysis through inverse propensity weighting). These include gender, age, learning disability, free lunch recipient, race, baseline grade level, GPA, baseline test performance (and within-baseline-school math test decile), days absent from school, disciplinary incidents, including suspensions, and arrests.

All plots and tables presented are estimated using the `GRF` algorithm estimated on the full analysis sample unless noted otherwise. We use split-sample estimation procedures to get estimates and confidence intervals for our calibration tests (splitsample quantities are denoted with '(split)').




\newpage

<!-- ## Section 1: with imputing block means for missing covariates -->
<!-- ```{r, results='asis', include=T, echo=F, fig.height=2} -->
<!-- final_forests_imputed %>% print_forests() -->

<!-- ``` -->

<!-- \newpage -->



<!-- # Decile Heatmaps -->

\blandscape
# Full Outcome Plot 

```{r, include=T, echo=F, fig.height=10, fig.width=15}
library(scales)


plot_data <- NULL

for (outcome in outcomes_of_interest_labels){
  
  # get fullsample calibration test
  plot_data <- plot_data %>%
    bind_rows(
      fullsample_models[[outcome]]$calibration_test %>%
        filter(term %in% 'differential.forest.prediction') %>% 
        select(est=estimate, lo=lower_CI_full, hi=upper_CI_full) %>% 
        mutate(type = 'fullsample', outcome=outcome)
      )
  
  # get splitsample calibration test
  plot_data <- plot_data %>%
    bind_rows(
      splitsample_models[[outcome]]$calibration_test %>%
        filter(term %in% 'differential.forest.prediction') %>% 
        select(est=estimate_median, lo=lower_CI_median, hi=upper_CI_median) %>% 
        mutate(type = 'splitsample', outcome=outcome)
    )
}


full_het_plot <- plot_data %>%
  #filter(outcome %in% names(outcome_and_label_list)[which(outcome_and_label_list %in% main_outcomes)]) %>% 
  ggplot(aes(y=est,
             x=factor(outcome, levels = unique(outcome)),
             color=outcome,
             group=factor(type, levels=unique(type)))) +
  geom_point(position = position_dodge(0.4)) +
  geom_errorbar(aes(ymin=lo, ymax=hi),
                width=0.6,
                position = position_dodge(0.4)) +
  geom_hline(yintercept = 1, linetype='dashed', alpha=0.5) + 
  geom_hline(yintercept = 0, linetype='dashed', alpha=0.5) +
  scale_x_discrete(labels = wrap_format(10)) + 
  ggtitle(label = 'Calibration Test: Detecting Heterogeneity',
          subtitle = paste0("For each outcome, the estimate and confidence intervals for the differential",
                            " forest prediction coefficient are shown for the full-sample (left) and split-sample procedure (right).",
                            " Horizontal lines at 1 and 0.")) +
  theme_bw() +   theme(legend.position='none') + 
  xlab('Outcome of interest') + ylab('Coefficient estimate')

print(full_het_plot)
```
\elandscape
\newpage

```{r, results='asis', include=T, echo=F, fig.height=3.5, fig.width=7,  warning=F}
# for (comparison in all_pte_quantile_plots){
#   
#   for (plot in comparison){
#     cat('\n')
#     print(plot)
#     cat('\n')
#   }
#       
#  
#     cat('\\newpage')
# }


for (outcome in names(outcome_and_label_list)[which(outcome_and_label_list %in% main_outcomes)]){#names(fullsample_models)){
  cat('\n ')
  cat('# Outcome: ', outcome, " \n")
  
  current_model <- fullsample_models[[outcome]]
  current_splitsample_model <- splitsample_models[[outcome]]
  
  model_item_names <- names(current_model)
  i = 0
  
  for (item in current_model){
    i = i+1
    # if there's a splitsample pvalue, add adjusted pvalue column
    current_name <- model_item_names[i]
    clean_name <- current_name %>% stringr::str_replace_all("_", " ")
    
    if (current_name %in% c('tau_df', 'subsample_ate_table'
                            # , 'quartile_heterogeneity_table', 'median_heterogeneity_table',
                            # "ISR_ITT_quartile_table_wave1", "ISR_ITT_quartile_table_wave2", "ISR_ITT_median_table_wave1", "ISR_ITT_median_table_wave2"
                            ,
                            "calibration_tests_naive_quantile_dummies",
                            "calibration_tests_naive_linear"
                            )){next}
    
    if (current_name %in% c("calibration_test",
                            "calibration_tests_naive_quantile_dummies",
                            "calibration_tests_naive_linear")){
      
      item <- item %>%
        mutate(lower_CI_full = estimate - 1.96*std.error,
                upper_CI_full = estimate + 1.96*std.error) %>% 
        rename('Estimate (full)' = estimate,
               'Lower CI (full)' = lower_CI_full,
               'Upper CI (full)' = upper_CI_full) %>%
        select(-std.error)
      
      
      # get same table from splitsample object
      splitsample_item <- current_splitsample_model[[current_name]] %>% select(1,
                                                                               "Estimate (split)" = estimate_median,
                                                                               'Lower CI (split)' = lower_CI_median,
                                                                               'Upper CI (split)' = upper_CI_median)
      
      item <- item %>% left_join(splitsample_item)
      
      colnames(item) <- colnames(item) %>% stringr::str_replace_all("_", " ")
      
      
      if (current_name %in% "calibration_tests_naive_linear"){
        item <- item %>% mutate(term = stringr::str_replace_all(term, "_", " "))
      }
      
    }
    
    #item <- item[[1]]
    
    if (class(item) %in% 'gg'){
      print(item)
    }
    if (class(item) %in% 'tbl_df'){
      
      temp_kable_table <- item %>%
        kable(booktabs=T, digits=3,
              escape=F,
              longtable=T,
              caption = paste0(clean_name, " - ", outcome)) 
      
      if (current_name %in% c("quartile_heterogeneity_table")){
        temp_kable_table <- temp_kable_table %>% 
          kable_styling(latex_options = c(#'striped',
          'HOLD_position', "repeat_header")) %>% 
          column_spec(1, width="27em") %>% 
          pack_rows(index=c(" " = 2,
                            "Other Outcomes" = length(outcomes_of_interest) + length(additional_table_outcomes),
                            "Baseline Variables" = length(table_baselines),
                            "ISR Mechanisms, End of First Program Year" = length(isr_outcome_labels_2014),
                            "ISR Mechanisms, End of Second Program Year" = length(isr_outcome_labels_2015)))
        
      } else if (current_name %in% "median_heterogeneity_table"){
        temp_kable_table <- temp_kable_table %>%
          kable_styling(latex_options = c(#'striped',
          'HOLD_position', "repeat_header")) %>% 
          column_spec(1, width="35em") %>% 
          pack_rows(index=c(" " = 2,
                            "Other Outcomes" = length(outcomes_of_interest) + length(additional_table_outcomes),
                            "Baseline Variables" = length(table_baselines),
                            "ISR Mechanisms, End of First Program Year" = length(isr_outcome_labels_2014),
                            "ISR Mechanisms, End of Second Program Year" = length(isr_outcome_labels_2015)))
        
      } else if(current_name %in% c("ISR_ITT_quartile_table_wave1", "ISR_ITT_quartile_table_wave2", "quartile_ITT_table")){
        temp_kable_table <- temp_kable_table %>% 
          kable_styling(latex_options = c(#'striped',
          'HOLD_position', "repeat_header")) %>% 
          column_spec(1, width="23em") %>% 
          column_spec(2:ncol(item), width='5em')
        
      } 
      else if (current_name %in% c("ISR_ITT_median_table_wave1", "ISR_ITT_median_table_wave2", "median_ITT_table")) {
        temp_kable_table <- temp_kable_table %>%
          kable_styling(latex_options = c(#'striped',
          'HOLD_position', "repeat_header")) %>% 
          column_spec(1, width="30em") %>% 
          column_spec(2:ncol(item), width='5em')
        
      }
      else {
        temp_kable_table <- temp_kable_table %>%
          kable_styling(latex_options = c('striped', 'HOLD_position')) %>% 
          column_spec(1, width="10em") %>% 
          column_spec(2:ncol(item), width='5em')
      }
      
      print(temp_kable_table)
    }
    
  }
 
  
   cat('\n')
   cat('\\newpage')
}

```


# Multiple-outcome Comparisons

```{r, results='asis', include=T, echo=F, fig.height=4.4, fig.width=7.5,  warning=F}
source('multi_outcome_heatmaps.R')
str_replace <- stringr::str_replace

for (comparison in all_multi_pte_comparisons){
  
  i=0
  names_of_items <- names(comparison)
  
  for (item in comparison){
    i = i+1
    cat('\n')
    if ('gg' %in% class(item)){
      print(item)
    }
    if ('tbl_df' %in% class(item)){
      #next
      cat('\\newpage')

      # now replace the names of the table to be more intuitive;
      names(item) <- names(item) %>%
        str_replace(' 1x1', ': Low X, Low Y') %>%
        str_replace(' 1x2', ': Low X, High Y') %>% 
        str_replace(' 2x1', ': High X, Low Y') %>% 
        str_replace(' 2x2', ': High X, High Y')
      
        
      if (names_of_items[i] %>% stringr::str_detect('ITT')){
        item %>%
        kable(booktabs=T, digits=3,
              escape=F,
              longtable=T,
              caption = names_of_items[i]) %>% 
        kable_styling(latex_options = c(#'striped',
        'scale_down',
          'HOLD_position', "repeat_header")) %>% 
        column_spec(1, width="32em") %>% 
        column_spec(2:ncol(item), width='4em') %>% print()
        
      } else { #it's the summary table
        item %>%
        kable(booktabs=T, digits=3,
              escape=F,
              longtable=T,
              caption = names_of_items[i]) %>% 
        kable_styling(latex_options = c(#'striped',
        'scale_down',
          'HOLD_position', "repeat_header")) %>% 
        column_spec(1, width="32em") %>% 
        column_spec(2:ncol(item), width='4em') %>% 
        pack_rows(index=c(" " = 3,
                          "Other Outcomes" = length(outcomes_of_interest) + length(additional_table_outcomes),
                          "Baseline Variables" = length(table_baselines),
                          "ISR Mechanisms, End of First Program Year" = length(isr_outcome_labels_2014),
                          "ISR Mechanisms, End of Second Program Year" = length(isr_outcome_labels_2015))) %>% print()
      }
      
    }
    cat('\n')
  }
      
 
    cat('\\newpage')
}
```